---
title: "Homework3"
author: "Ezgi ORAL"
date: "28 12 2020"
output: html_document
---

```{r,echo=FALSE,results="hide"}
library(ie2misc)
library(dplyr)
library(readr)
require(utils)
library(lubridate)
library(glmnet)
```

## Reading the Data:
```{r}
hw3ConsData<-read_csv("GercekZamanliTuketim-01012016-01122020.csv")
```

## PART A

Naïve approaches to predict next day’s consumption:

```{r}
indexPartA<-which(hw3ConsData$Tarih=="01.11.2020") # Start Data
temp_lag168<-hw3ConsData[(indexPartA[1] - 168):(nrow(hw3ConsData)-168),]
dataForPartA_lag168 <- cbind(hw3ConsData[(indexPartA[1]):(nrow(hw3ConsData)),],temp_lag168)
head(dataForPartA_lag168)
temp_lag48<-hw3ConsData[(indexPartA[1] - 48):(nrow(hw3ConsData)-48),]
dataForPartA_lag48 <- cbind(hw3ConsData[(indexPartA[1]):(nrow(hw3ConsData)),],temp_lag48)
head(dataForPartA_lag48)
```

Since we have calculated the predictions, now we can compare these values with the real consumption values.

```{r}
mape_lag168 <- mape(as.numeric(dataForPartA_lag168[,6]) , dataForPartA_lag168[,3])
summary(mape_lag168)
mape_lag48 <- mape(dataForPartA_lag48[,6] , dataForPartA_lag48[,3])
summary(mape_lag48)
```

We see that lag_168 has a "Mape" value of 3.449% and lag_48 has a "Mape" value of 8.06%. This means that the prediction made by using lag_168 is better than lag_48. This makes sense because intuitively we would expect the same result. For example when we compare Sunday's "routine" with Friday's "routine" and last Sunday's "routine", we expect more resemblance in last Sunday's "routine". 

When we look at both predictions, we can say that they are good predictions because their Mape values are under 10%.


## PART B

Now, we apply the linear regression model. Due to daylight savings program applied on 27.03.2016, some data are missing. Therefore we discard the day from the training data.
```{r}
startB<-cbind(dataForPartA_lag48,dataForPartA_lag168[,6])
startB<-startB[,c(3,6,7)]
colnames(startB)<-c("A", "B","C")

dataForPartB <- cbind(hw3ConsData[169:(indexPartA[1]-1),],hw3ConsData[121:(indexPartA[1]-49),],hw3ConsData[1:(indexPartA[1]-169),])

dataForPartB<-dataForPartB[-which(dataForPartB[,1]=="27.03.2016"),]
dataForPartB<-dataForPartB[-which(dataForPartB[,4]=="27.03.2016"),]
dataForPartB<-dataForPartB[-which(dataForPartB[,7]=="27.03.2016"),]

dataForPartB<-dataForPartB[,c(1,2,3,6,9)]

colnames(dataForPartB)<-c("Date", "Hour", "Data Real", "Data lag_48","Data lag_168")
```

Long format:

```{r}
head(dataForPartB)

linearFit_bothLagsPartB <- lm(`Data Real`~.,data=dataForPartB[,c(3,4,5)])
summary(linearFit_bothLagsPartB) 

testB<- as.data.frame(cbind(startB$B,startB$C))
colnames(testB)<-c("Data lag_48","Data lag_168")
estimatePartB<-(predict(linearFit_bothLagsPartB, newdata = testB))

b<-data.frame(dataForPartA_lag168[,3])

ww<-cbind(estimatePartB,b)
mapePartB<- mape(ww[,1],ww[,2])
summary(mapePartB)    
```

We can observe all the necessary coefficients for the linear regression model that we obtained. Both lag_48 and lag_168 features are used and the intercept is also included.

When we look at the "Mape" result, it is 4.231%. We observe that this prediction model is good because it is under 10%. When we compare this result with Part A, we see that the linear regression model is better than lag_48 naive approach however, lag_168 naive approach is better than the linear regression model.

## PART C

Now, we take the hourly seasonality into account. So, we model each hour separately as follows:

```{r}
elements <- matrix(0,(nrow(dataForPartB)/24),24)

for (i in 1:24)
{
  elements[,i]<-which((as.numeric(dataForPartB$Hour)/3600)==(i-1))
}
combinedDataForPartC_0h<-dataForPartB[elements[,1],] # 
linearFit_bothLags_0h <- lm(`Data Real`~.,data=combinedDataForPartC_0h[,c(3,4,5)])  
summary(linearFit_bothLags_0h) 

test_0h<-dataForPartB[seq(1,nrow(dataForPartB)-23, by = 24),c(4,5)]
estimatePartc_0h<-(predict(linearFit_bothLags_0h, newdata = test_0h))

tempC_0h <- as.data.frame(cbind(estimatePartc_0h,combinedDataForPartC_0h[,3]))
mapePartC_0h <- mape(tempC_0h[,1],tempC_0h[,2])
summary(mapePartC_0h)


combinedDataForPartC_1h<-dataForPartB[elements[,2],]
linearFit_bothLags_1h <- lm(`Data Real`~.,data=combinedDataForPartC_1h[,c(3,4,5)])  
summary(linearFit_bothLags_1h) 
test_1h<- dataForPartB[seq(2,nrow(dataForPartB)-22, by = 24),]
estimatePartc_1h<-(predict(linearFit_bothLags_1h, newdata = test_1h))
tempC_1h <- as.data.frame(cbind(estimatePartc_1h,combinedDataForPartC_1h[,3]))
mapePartC_1h <- mape(tempC_1h[,1],tempC_1h[,2])
summary(mapePartC_1h)


combinedDataForPartC_2h<-dataForPartB[elements[,3],]
linearFit_bothLags_2h <- lm(`Data Real`~.,data=combinedDataForPartC_2h[,c(3,4,5)])  
summary(linearFit_bothLags_2h) 
test_2h<- dataForPartB[seq(3,nrow(dataForPartB)-21, by = 24),]
estimatePartc_2h<-(predict(linearFit_bothLags_2h, newdata = test_2h))
tempC_2h <- as.data.frame(cbind(estimatePartc_2h,combinedDataForPartC_2h[,3]))
mapePartC_2h <- mape(tempC_2h[,1],tempC_2h[,2])
summary(mapePartC_2h)

combinedDataForPartC_3h<-dataForPartB[elements[,4],]
linearFit_bothLags_3h <- lm(`Data Real`~.,data=combinedDataForPartC_3h[,c(3,4,5)])  
summary(linearFit_bothLags_3h) 
test_3h<- dataForPartB[seq(4,nrow(dataForPartB)-20, by = 24),]
estimatePartc_3h<-(predict(linearFit_bothLags_3h, newdata = test_3h))
tempC_3h <- as.data.frame(cbind(estimatePartc_3h,combinedDataForPartC_3h[,3]))
mapePartC_3h <- mape(tempC_3h[,1],tempC_3h[,2])
summary(mapePartC_3h)

combinedDataForPartC_4h<-dataForPartB[elements[,5],]
linearFit_bothLags_4h <- lm(`Data Real`~.,data=combinedDataForPartC_4h[,c(3,4,5)])  
summary(linearFit_bothLags_4h) 
test_4h<- dataForPartB[seq(5,nrow(dataForPartB)-19, by = 24),]
estimatePartc_4h<-(predict(linearFit_bothLags_4h, newdata = test_4h))
tempC_4h <- as.data.frame(cbind(estimatePartc_4h,combinedDataForPartC_4h[,3]))
mapePartC_4h <- mape(tempC_4h[,1],tempC_4h[,2])
summary(mapePartC_4h)


combinedDataForPartC_5h<-dataForPartB[elements[,6],]
linearFit_bothLags_5h <- lm(`Data Real`~.,data=combinedDataForPartC_5h[,c(3,4,5)])  
summary(linearFit_bothLags_5h) 
test_5h<- dataForPartB[seq(6,nrow(dataForPartB)-18, by = 24),]
estimatePartc_5h<-(predict(linearFit_bothLags_5h, newdata = test_5h))
tempC_5h <- as.data.frame(cbind(estimatePartc_5h,combinedDataForPartC_5h[,3]))
mapePartC_5h <- mape(tempC_5h[,1],tempC_5h[,2])
summary(mapePartC_5h)

combinedDataForPartC_6h<-dataForPartB[elements[,7],]
linearFit_bothLags_6h <- lm(`Data Real`~.,data=combinedDataForPartC_6h[,c(3,4,5)])  
summary(linearFit_bothLags_6h) 
test_6h<- dataForPartB[seq(7,nrow(dataForPartB)-17, by = 24),]
estimatePartc_6h<-(predict(linearFit_bothLags_6h, newdata = test_6h))
tempC_6h <- as.data.frame(cbind(estimatePartc_6h,combinedDataForPartC_6h[,3]))
mapePartC_6h <- mape(tempC_6h[,1],tempC_6h[,2])
summary(mapePartC_6h)

combinedDataForPartC_7h<-dataForPartB[elements[,8],]
linearFit_bothLags_7h <- lm(`Data Real`~.,data=combinedDataForPartC_7h[,c(3,4,5)])  
summary(linearFit_bothLags_7h) 
test_7h<- dataForPartB[seq(8,nrow(dataForPartB)-16, by = 24),]
estimatePartc_7h<-(predict(linearFit_bothLags_7h, newdata = test_7h))
tempC_7h <- as.data.frame(cbind(estimatePartc_7h,combinedDataForPartC_7h[,3]))
mapePartC_7h <- mape(tempC_7h[,1],tempC_7h[,2])
summary(mapePartC_7h)

combinedDataForPartC_8h<-dataForPartB[elements[,9],]
linearFit_bothLags_8h <- lm(`Data Real`~.,data=combinedDataForPartC_8h[,c(3,4,5)])  
summary(linearFit_bothLags_8h) 
test_8h<- dataForPartB[seq(9,nrow(dataForPartB)-15, by = 24),]
estimatePartc_8h<-(predict(linearFit_bothLags_8h, newdata = test_8h))
tempC_8h <- as.data.frame(cbind(estimatePartc_8h,combinedDataForPartC_8h[,3]))
mapePartC_8h <- mape(tempC_8h[,1],tempC_8h[,2])
summary(mapePartC_8h)

combinedDataForPartC_9h<-dataForPartB[elements[,10],]
linearFit_bothLags_9h <- lm(`Data Real`~.,data=combinedDataForPartC_9h[,c(3,4,5)])  
summary(linearFit_bothLags_9h) 
test_9h<- dataForPartB[seq(10,nrow(dataForPartB)-14, by = 24),]
estimatePartc_9h<-(predict(linearFit_bothLags_9h, newdata = test_9h))
tempC_9h <- as.data.frame(cbind(estimatePartc_9h,combinedDataForPartC_9h[,3]))
mapePartC_9h <- mape(tempC_9h[,1],tempC_9h[,2])
summary(mapePartC_9h)

combinedDataForPartC_10h<-dataForPartB[elements[,11],]
linearFit_bothLags_10h <- lm(`Data Real`~.,data=combinedDataForPartC_10h[,c(3,4,5)])  
summary(linearFit_bothLags_10h) 
test_10h<- dataForPartB[seq(11,nrow(dataForPartB)-13, by = 24),]
estimatePartc_10h<-(predict(linearFit_bothLags_10h, newdata = test_10h))
tempC_10h <- as.data.frame(cbind(estimatePartc_10h,combinedDataForPartC_10h[,3]))
mapePartC_10h <- mape(tempC_10h[,1],tempC_10h[,2])
summary(mapePartC_10h)

combinedDataForPartC_11h<-dataForPartB[elements[,12],]
linearFit_bothLags_11h <- lm(`Data Real`~.,data=combinedDataForPartC_11h[,c(3,4,5)])  
summary(linearFit_bothLags_11h) 
test_11h<- dataForPartB[seq(12,nrow(dataForPartB)-12, by = 24),]
estimatePartc_11h<-(predict(linearFit_bothLags_11h, newdata = test_11h))
tempC_11h <- as.data.frame(cbind(estimatePartc_11h,combinedDataForPartC_11h[,3]))
mapePartC_11h <- mape(tempC_11h[,1],tempC_11h[,2])
summary(mapePartC_11h)

combinedDataForPartC_12h<-dataForPartB[elements[,13],]
linearFit_bothLags_12h <- lm(`Data Real`~.,data=combinedDataForPartC_12h[,c(3,4,5)])  
summary(linearFit_bothLags_12h) 
test_12h<- dataForPartB[seq(13,nrow(dataForPartB)-11, by = 24),]
estimatePartc_12h<-(predict(linearFit_bothLags_12h, newdata = test_12h))
tempC_12h <- as.data.frame(cbind(estimatePartc_12h,combinedDataForPartC_12h[,3]))
mapePartC_12h <- mape(tempC_12h[,1],tempC_12h[,2])
summary(mapePartC_12h)

combinedDataForPartC_13h<-dataForPartB[elements[,14],]
linearFit_bothLags_13h <- lm(`Data Real`~.,data=combinedDataForPartC_13h[,c(3,4,5)])  
summary(linearFit_bothLags_13h) 
test_13h<- dataForPartB[seq(14,nrow(dataForPartB)-10, by = 24),]
estimatePartc_13h<-(predict(linearFit_bothLags_13h, newdata = test_13h))
tempC_13h <- as.data.frame(cbind(estimatePartc_13h,combinedDataForPartC_13h[,3]))
mapePartC_13h <- mape(tempC_13h[,1],tempC_13h[,2])
summary(mapePartC_13h)

combinedDataForPartC_14h<-dataForPartB[elements[,15],]
linearFit_bothLags_14h <- lm(`Data Real`~.,data=combinedDataForPartC_14h[,c(3,4,5)])  
summary(linearFit_bothLags_14h) 
test_14h<- dataForPartB[seq(15,nrow(dataForPartB)-9, by = 24),]
estimatePartc_14h<-(predict(linearFit_bothLags_14h, newdata = test_14h))
tempC_14h <- as.data.frame(cbind(estimatePartc_14h,combinedDataForPartC_14h[,3]))
mapePartC_14h <- mape(tempC_14h[,1],tempC_14h[,2])
summary(mapePartC_14h)

combinedDataForPartC_15h<-dataForPartB[elements[,16],]
linearFit_bothLags_15h <- lm(`Data Real`~.,data=combinedDataForPartC_15h[,c(3,4,5)])  
summary(linearFit_bothLags_15h) 
test_15h<- dataForPartB[seq(16,nrow(dataForPartB)-8, by = 24),]
estimatePartc_15h<-(predict(linearFit_bothLags_15h, newdata = test_15h))
tempC_15h <- as.data.frame(cbind(estimatePartc_15h,combinedDataForPartC_15h[,3]))
mapePartC_15h <- mape(tempC_15h[,1],tempC_15h[,2])
summary(mapePartC_15h)

combinedDataForPartC_16h<-dataForPartB[elements[,17],]
linearFit_bothLags_16h <- lm(`Data Real`~.,data=combinedDataForPartC_16h[,c(3,4,5)])  
summary(linearFit_bothLags_16h) 
test_16h<- dataForPartB[seq(17,nrow(dataForPartB)-7, by = 24),]
estimatePartc_16h<-(predict(linearFit_bothLags_16h, newdata = test_16h))
tempC_16h <- as.data.frame(cbind(estimatePartc_16h,combinedDataForPartC_16h[,3]))
mapePartC_16h <- mape(tempC_16h[,1],tempC_16h[,2])
summary(mapePartC_16h)

combinedDataForPartC_17h<-dataForPartB[elements[,18],]
linearFit_bothLags_17h <- lm(`Data Real`~.,data=combinedDataForPartC_17h[,c(3,4,5)])  
summary(linearFit_bothLags_17h) 
test_17h<- dataForPartB[seq(18,nrow(dataForPartB)-6, by = 24),]
estimatePartc_17h<-(predict(linearFit_bothLags_17h, newdata = test_17h))
tempC_17h <- as.data.frame(cbind(estimatePartc_17h,combinedDataForPartC_17h[,3]))
mapePartC_17h <- mape(tempC_17h[,1],tempC_17h[,2])
summary(mapePartC_17h)

combinedDataForPartC_18h<-dataForPartB[elements[,19],]
linearFit_bothLags_18h <- lm(`Data Real`~.,data=combinedDataForPartC_18h[,c(3,4,5)])  
summary(linearFit_bothLags_18h) 
test_18h<- dataForPartB[seq(19,nrow(dataForPartB)-5, by = 24),]
estimatePartc_18h<-(predict(linearFit_bothLags_18h, newdata = test_18h))
tempC_18h <- as.data.frame(cbind(estimatePartc_18h,combinedDataForPartC_18h[,3]))
mapePartC_18h <- mape(tempC_18h[,1],tempC_18h[,2])
summary(mapePartC_18h)

combinedDataForPartC_19h<-dataForPartB[elements[,20],]
linearFit_bothLags_19h <- lm(`Data Real`~.,data=combinedDataForPartC_19h[,c(3,4,5)])  
summary(linearFit_bothLags_19h) 
test_19h<- dataForPartB[seq(20,nrow(dataForPartB)-4, by = 24),]
estimatePartc_19h<-(predict(linearFit_bothLags_19h, newdata = test_19h))
tempC_19h <- as.data.frame(cbind(estimatePartc_19h,combinedDataForPartC_19h[,3]))
mapePartC_19h <- mape(tempC_19h[,1],tempC_19h[,2])
summary(mapePartC_19h)

combinedDataForPartC_20h<-dataForPartB[elements[,21],]
linearFit_bothLags_20h <- lm(`Data Real`~.,data=combinedDataForPartC_20h[,c(3,4,5)])  
summary(linearFit_bothLags_20h) 
test_20h<- dataForPartB[seq(21,nrow(dataForPartB)-3, by = 24),]
estimatePartc_20h<-(predict(linearFit_bothLags_20h, newdata = test_20h))
tempC_20h <- as.data.frame(cbind(estimatePartc_20h,combinedDataForPartC_20h[,3]))
mapePartC_20h <- mape(tempC_20h[,1],tempC_20h[,2])
summary(mapePartC_20h)

combinedDataForPartC_21h<-dataForPartB[elements[,22],]
linearFit_bothLags_21h <- lm(`Data Real`~.,data=combinedDataForPartC_21h[,c(3,4,5)])  
summary(linearFit_bothLags_21h) 
test_21h<- dataForPartB[seq(22,nrow(dataForPartB)-2, by = 24),]
estimatePartc_21h<-(predict(linearFit_bothLags_21h, newdata = test_21h))
tempC_21h <- as.data.frame(cbind(estimatePartc_21h,combinedDataForPartC_21h[,3]))
mapePartC_21h <- mape(tempC_21h[,1],tempC_21h[,2])
summary(mapePartC_21h)

combinedDataForPartC_22h<-dataForPartB[elements[,23],]
linearFit_bothLags_22h <- lm(`Data Real`~.,data=combinedDataForPartC_22h[,c(3,4,5)])  
summary(linearFit_bothLags_22h) 
test_22h<- dataForPartB[seq(23,nrow(dataForPartB)-1, by = 24),]
estimatePartc_22h<-(predict(linearFit_bothLags_22h, newdata = test_22h))
tempC_22h <- as.data.frame(cbind(estimatePartc_22h,combinedDataForPartC_22h[,3]))
mapePartC_22h <- mape(tempC_22h[,1],tempC_22h[,2])
summary(mapePartC_22h)

combinedDataForPartC_23h<-dataForPartB[elements[,24],]
linearFit_bothLags_23h <- lm(`Data Real`~.,data=combinedDataForPartC_23h[,c(3,4,5)])  
summary(linearFit_bothLags_23h) 
test_23h<- dataForPartB[seq(24,nrow(dataForPartB), by = 24),]
estimatePartc_23h<-(predict(linearFit_bothLags_23h, newdata = test_23h))
tempC_23h <- as.data.frame(cbind(estimatePartc_23h,combinedDataForPartC_23h[,3]))
mapePartC_23h <- mape(tempC_23h[,1],tempC_23h[,2])
summary(mapePartC_23h)

mapePartC<-rbind(mapePartC_0h,mapePartC_1h,mapePartC_2h, mapePartC_3h,mapePartC_4h,mapePartC_5h,mapePartC_6h,mapePartC_7h,mapePartC_8h,mapePartC_9h,mapePartC_10h,mapePartC_11h,mapePartC_12h,mapePartC_13h,mapePartC_14h,mapePartC_15h,mapePartC_16h,mapePartC_17h,mapePartC_18h,mapePartC_19h,mapePartC_20h,mapePartC_21h,mapePartC_22h,mapePartC_23h)
mapePartC
```

Above, we can see the "Mape" values for each hour.
These results tell us why hourly seasonality is important. For night time (20.00 - 05.00), our predictions are superior, and for working hours (09.00 - 16.00) are inferior. However, all these predictions can be accepted as a good prediction because their "Mape" values are lower than 10%.

When we compare these values, we see that they are all better than lag_48 naive approach. However, some values (especially working hours) have worse performances than lag_168 naive approach.

Also, we observe that the coefficients in each hour are similar to each other. There is not any major difference. However, we can say that there is a direct relationship between the Intercept value and the Mape value.

## PART D

Now, we apply penalized model (lasso regression) for each hour:

```{r}
dataForPart<-as.numeric(dataForPartB$Hour)/3600

partD_0h<-dataForPartB[which(dataForPart==0),]
colnames(partD_0h)<-c("Date", "Hour", "Data Real 0h", "Data lag_48 0h","Data lag_168 0h")

partD_1h<-dataForPartB[which(dataForPart==1),]
colnames(partD_1h)<-c("Date", "Hour", "Data Real 1h", "Data lag_48 1h","Data lag_168 1h")

partD_2h<-dataForPartB[which(dataForPart==2),]
colnames(partD_2h)<-c("Date", "Hour", "Data Real 2h", "Data lag_48 2h","Data lag_168 2h")

partD_3h<-dataForPartB[which(dataForPart==3),]
colnames(partD_3h)<-c("Date", "Hour", "Data Real 3h", "Data lag_48 3h","Data lag_168 3h")

partD_4h<-dataForPartB[which(dataForPart==4),]
colnames(partD_4h)<-c("Date", "Hour", "Data Real 4h", "Data lag_48 4h","Data lag_168 4h")

partD_5h<-dataForPartB[which(dataForPart==5),]
colnames(partD_5h)<-c("Date", "Hour", "Data Real 5h", "Data lag_48 5h","Data lag_168 5h")

partD_6h<-dataForPartB[which(dataForPart==6),]
colnames(partD_6h)<-c("Date", "Hour", "Data Real 6h", "Data lag_48 6h","Data lag_168 6h")

partD_7h<-dataForPartB[which(dataForPart==7),]
colnames(partD_7h)<-c("Date", "Hour", "Data Real 7h", "Data lag_48 7h","Data lag_168 7h")

partD_8h<-dataForPartB[which(dataForPart==8),]
colnames(partD_8h)<-c("Date", "Hour", "Data Real 8h", "Data lag_48 8h","Data lag_168 8h")

partD_9h<-dataForPartB[which(dataForPart==9),]
colnames(partD_9h)<-c("Date", "Hour", "Data Real 9h", "Data lag_48 9h","Data lag_168 9h")

partD_10h<-dataForPartB[which(dataForPart==10),]
colnames(partD_10h)<-c("Date", "Hour", "Data Real 10h", "Data lag_48 10h","Data lag_168 10h")

partD_11h<-dataForPartB[which(dataForPart==11),]
colnames(partD_11h)<-c("Date", "Hour", "Data Real 11h", "Data lag_48 11h","Data lag_168 11h")

partD_12h<-dataForPartB[which(dataForPart==12),]
colnames(partD_12h)<-c("Date", "Hour", "Data Real 12h", "Data lag_48 12h","Data lag_168 12h")

partD_13h<-dataForPartB[which(dataForPart==13),]
colnames(partD_13h)<-c("Date", "Hour", "Data Real 13h", "Data lag_48 13h","Data lag_168 13h")

partD_14h<-dataForPartB[which(dataForPart==14),]
colnames(partD_14h)<-c("Date", "Hour", "Data Real 14h", "Data lag_48 14h","Data lag_168 14h")

partD_15h<-dataForPartB[which(dataForPart==15),]
colnames(partD_15h)<-c("Date", "Hour", "Data Real 15h", "Data lag_48 15h","Data lag_168 15h")

partD_16h<-dataForPartB[which(dataForPart==16),]
colnames(partD_16h)<-c("Date", "Hour", "Data Real 16h", "Data lag_48 16h","Data lag_168 16h")

partD_17h<-dataForPartB[which(dataForPart==17),]
colnames(partD_17h)<-c("Date", "Hour", "Data Real 17h", "Data lag_48 17h","Data lag_168 17h")

partD_18h<-dataForPartB[which(dataForPart==18),]
colnames(partD_18h)<-c("Date", "Hour", "Data Real 18h", "Data lag_48 18h","Data lag_168 18h")

partD_19h<-dataForPartB[which(dataForPart==19),]
colnames(partD_19h)<-c("Date", "Hour", "Data Real 19h", "Data lag_48 19h","Data lag_168 19h")

partD_20h<-dataForPartB[which(dataForPart==20),]
colnames(partD_20h)<-c("Date", "Hour", "Data Real 20h", "Data lag_48 20h","Data lag_168 20h")

partD_21h<-dataForPartB[which(dataForPart==21),]
colnames(partD_21h)<-c("Date", "Hour", "Data Real 21h", "Data lag_48 21h","Data lag_168 21h")

partD_22h<-dataForPartB[which(dataForPart==22),]
colnames(partD_22h)<-c("Date", "Hour", "Data Real 22h", "Data lag_48 22h","Data lag_168 22h")

partD_23h<-dataForPartB[which(dataForPart==23),]
colnames(partD_23h)<-c("Date", "Hour", "Data Real 23h", "Data lag_48 23h","Data lag_168 23h")

wideFirstStep<-cbind(partD_0h[,c(1,4,5)],partD_1h[,c(4,5)],partD_2h[,c(4,5)],partD_3h[,c(4,5)],partD_4h[,c(4,5)],partD_5h[,c(4,5)],partD_6h[,c(4,5)],partD_7h[,c(4,5)],partD_8h[,c(4,5)],partD_9h[,c(4,5)],partD_10h[,c(4,5)],partD_11h[,c(4,5)],partD_12h[,c(4,5)],partD_13h[,c(4,5)],partD_14h[,c(4,5)],partD_15h[,c(4,5)],partD_16h[,c(4,5)],partD_17h[,c(4,5)],partD_18h[,c(4,5)],partD_19h[,c(4,5)],partD_20h[,c(4,5)],partD_21h[,c(4,5)],partD_22h[,c(4,5)],partD_23h[,c(4,5)] )

wideDataTrain<-cbind(wideFirstStep,partD_0h[,3])


tempPartD_<-cbind(dataForPartA_lag48[,c(1,2,3,6)],dataForPartA_lag168[,6])
colnames(tempPartD_)<-c("Date", "Hour", "Data Real", "Data lag_48","Data lag_168")

dataPartD_numeric <-as.numeric(tempPartD_$Hour)/3600

tempPartD_0h<-tempPartD_[which(dataPartD_numeric==0),]
colnames(tempPartD_0h)<-c("Date", "Hour", "Data Real 0h", "Data lag_48 0h","Data lag_168 0h")
tempPartD_1h<-tempPartD_[which(dataPartD_numeric==1),]
colnames(tempPartD_1h)<-c("Date", "Hour", "Data Real 1h", "Data lag_48 1h","Data lag_168 1h")
tempPartD_2h<-tempPartD_[which(dataPartD_numeric==2),]
colnames(tempPartD_2h)<-c("Date", "Hour", "Data Real 2h", "Data lag_48 2h","Data lag_168 2h")
tempPartD_3h<-tempPartD_[which(dataPartD_numeric==3),]
colnames(tempPartD_3h)<-c("Date", "Hour", "Data Real 3h", "Data lag_48 3h","Data lag_168 3h")
tempPartD_4h<-tempPartD_[which(dataPartD_numeric==4),]
colnames(tempPartD_4h)<-c("Date", "Hour", "Data Real 4h", "Data lag_48 4h","Data lag_168 4h")
tempPartD_5h<-tempPartD_[which(dataPartD_numeric==5),]
colnames(tempPartD_5h)<-c("Date", "Hour", "Data Real 5h", "Data lag_48 5h","Data lag_168 5h")
tempPartD_6h<-tempPartD_[which(dataPartD_numeric==6),]
colnames(tempPartD_6h)<-c("Date", "Hour", "Data Real 6h", "Data lag_48 6h","Data lag_168 6h")
tempPartD_7h<-tempPartD_[which(dataPartD_numeric==7),]
colnames(tempPartD_7h)<-c("Date", "Hour", "Data Real 7h", "Data lag_48 7h","Data lag_168 7h")
tempPartD_8h<-tempPartD_[which(dataPartD_numeric==8),]
colnames(tempPartD_8h)<-c("Date", "Hour", "Data Real 8h", "Data lag_48 8h","Data lag_168 8h")
tempPartD_9h<-tempPartD_[which(dataPartD_numeric==9),]
colnames(tempPartD_9h)<-c("Date", "Hour", "Data Real 9h", "Data lag_48 9h","Data lag_168 9h")
tempPartD_10h<-tempPartD_[which(dataPartD_numeric==10),]
colnames(tempPartD_10h)<-c("Date", "Hour", "Data Real 10h", "Data lag_48 10h","Data lag_168 10h")
tempPartD_11h<-tempPartD_[which(dataPartD_numeric==11),]
colnames(tempPartD_11h)<-c("Date", "Hour", "Data Real 11h", "Data lag_48 11h","Data lag_168 11h")
tempPartD_12h<-tempPartD_[which(dataPartD_numeric==12),]
colnames(tempPartD_12h)<-c("Date", "Hour", "Data Real 12h", "Data lag_48 12h","Data lag_168 12h")
tempPartD_13h<-tempPartD_[which(dataPartD_numeric==13),]
colnames(tempPartD_13h)<-c("Date", "Hour", "Data Real 13h", "Data lag_48 13h","Data lag_168 13h")
tempPartD_14h<-tempPartD_[which(dataPartD_numeric==14),]
colnames(tempPartD_14h)<-c("Date", "Hour", "Data Real 14h", "Data lag_48 14h","Data lag_168 14h")
tempPartD_15h<-tempPartD_[which(dataPartD_numeric==15),]
colnames(tempPartD_15h)<-c("Date", "Hour", "Data Real 15h", "Data lag_48 15h","Data lag_168 15h")
tempPartD_16h<-tempPartD_[which(dataPartD_numeric==16),]
colnames(tempPartD_16h)<-c("Date", "Hour", "Data Real 16h", "Data lag_48 16h","Data lag_168 16h")
tempPartD_17h<-tempPartD_[which(dataPartD_numeric==17),]
colnames(tempPartD_17h)<-c("Date", "Hour", "Data Real 17h", "Data lag_48 17h","Data lag_168 17h")
tempPartD_18h<-tempPartD_[which(dataPartD_numeric==18),]
colnames(tempPartD_18h)<-c("Date", "Hour", "Data Real 18h", "Data lag_48 18h","Data lag_168 18h")
tempPartD_19h<-tempPartD_[which(dataPartD_numeric==19),]
colnames(tempPartD_19h)<-c("Date", "Hour", "Data Real 19h", "Data lag_48 19h","Data lag_168 19h")
tempPartD_20h<-tempPartD_[which(dataPartD_numeric==20),]
colnames(tempPartD_20h)<-c("Date", "Hour", "Data Real 20h", "Data lag_48 20h","Data lag_168 20h")
tempPartD_21h<-tempPartD_[which(dataPartD_numeric==21),]
colnames(tempPartD_21h)<-c("Date", "Hour", "Data Real 21h", "Data lag_48 21h","Data lag_168 21h")
tempPartD_22h<-tempPartD_[which(dataPartD_numeric==22),]
colnames(tempPartD_22h)<-c("Date", "Hour", "Data Real 22h", "Data lag_48 22h","Data lag_168 22h")
tempPartD_23h<-tempPartD_[which(dataPartD_numeric==23),]
colnames(tempPartD_23h)<-c("Date", "Hour", "Data Real 23h", "Data lag_48 23h","Data lag_168 23h")

wideTestData<-cbind(tempPartD_0h[,c(1,4,5)],tempPartD_1h[,c(4,5)],tempPartD_2h[,c(4,5)],tempPartD_3h[,c(4,5)],tempPartD_4h[,c(4,5)],tempPartD_5h[,c(4,5)],tempPartD_6h[,c(4,5)],tempPartD_7h[,c(4,5)],tempPartD_8h[,c(4,5)],tempPartD_9h[,c(4,5)],tempPartD_10h[,c(4,5)],tempPartD_11h[,c(4,5)],tempPartD_12h[,c(4,5)],tempPartD_13h[,c(4,5)],tempPartD_14h[,c(4,5)],tempPartD_15h[,c(4,5)],tempPartD_16h[,c(4,5)],tempPartD_17h[,c(4,5)],tempPartD_18h[,c(4,5)],tempPartD_19h[,c(4,5)],tempPartD_20h[,c(4,5)],tempPartD_21h[,c(4,5)],tempPartD_22h[,c(4,5)],tempPartD_23h[,c(4,5)] )
```

Lasso regression calculations:

```{r}
lambdaCalc<-cv.glmnet(as.matrix(wideDataTrain[,-c(1,50)]), partD_0h[,3], type.measure='mse', nfolds=10, family='gaussian', alpha=1)$lambda.min
praModel_0h<-glmnet(as.matrix(wideDataTrain[,-c(1,50)]),partD_0h[,3],alpha=1,family='gaussian',lambda = lambdaCalc)
predict_0h<-predict(praModel_0h, newx= as.matrix(wideTestData[,-c(1)])) 

lambdaCalc<-cv.glmnet(as.matrix(wideDataTrain[,-c(1,50)]), partD_1h[,3], type.measure='mse', nfolds=10, family='gaussian', alpha=1)$lambda.min
praModel_1h<-glmnet(as.matrix(wideDataTrain[,-c(1,50)]),partD_1h[,3],alpha=1,family='gaussian',lambda = lambdaCalc)
predict_1h<-predict(praModel_1h, newx= as.matrix(wideTestData[,-c(1)]))

lambdaCalc<-cv.glmnet(as.matrix(wideDataTrain[,-c(1,50)]), partD_2h[,3], type.measure='mse', nfolds=10, family='gaussian', alpha=1)$lambda.min
praModel_2h<-glmnet(as.matrix(wideDataTrain[,-c(1,50)]),partD_2h[,3],alpha=1,family='gaussian',lambda = lambdaCalc)
predict_2h<-predict(praModel_2h, newx= as.matrix(wideTestData[,-c(1)]))

lambdaCalc<-cv.glmnet(as.matrix(wideDataTrain[,-c(1,50)]), partD_3h[,3], type.measure='mse', nfolds=10, family='gaussian', alpha=1)$lambda.min
praModel_3h<-glmnet(as.matrix(wideDataTrain[,-c(1,50)]),partD_3h[,3],alpha=1,family='gaussian',lambda = lambdaCalc)
predict_3h<-predict(praModel_3h, newx= as.matrix(wideTestData[,-c(1)]))

lambdaCalc<-cv.glmnet(as.matrix(wideDataTrain[,-c(1,50)]), partD_4h[,3], type.measure='mse', nfolds=10, family='gaussian', alpha=1)$lambda.min
praModel_4h<-glmnet(as.matrix(wideDataTrain[,-c(1,50)]),partD_4h[,3],alpha=1,family='gaussian',lambda = lambdaCalc)
predict_4h<-predict(praModel_4h, newx= as.matrix(wideTestData[,-c(1)]))

lambdaCalc<-cv.glmnet(as.matrix(wideDataTrain[,-c(1,50)]), partD_5h[,3], type.measure='mse', nfolds=10, family='gaussian', alpha=1)$lambda.min
praModel_5h<-glmnet(as.matrix(wideDataTrain[,-c(1,50)]),partD_5h[,3],alpha=1,family='gaussian',lambda = lambdaCalc)
predict_5h<-predict(praModel_5h, newx= as.matrix(wideTestData[,-c(1)]))

lambdaCalc<-cv.glmnet(as.matrix(wideDataTrain[,-c(1,50)]), partD_6h[,3], type.measure='mse', nfolds=10, family='gaussian', alpha=1)$lambda.min
praModel_6h<-glmnet(as.matrix(wideDataTrain[,-c(1,50)]),partD_6h[,3],alpha=1,family='gaussian',lambda = lambdaCalc)
predict_6h<-predict(praModel_6h, newx= as.matrix(wideTestData[,-c(1)]))

lambdaCalc<-cv.glmnet(as.matrix(wideDataTrain[,-c(1,50)]), partD_7h[,3], type.measure='mse', nfolds=10, family='gaussian', alpha=1)$lambda.min
praModel_7h<-glmnet(as.matrix(wideDataTrain[,-c(1,50)]),partD_7h[,3],alpha=1,family='gaussian',lambda = lambdaCalc)
predict_7h<-predict(praModel_7h, newx= as.matrix(wideTestData[,-c(1)]))

lambdaCalc<-cv.glmnet(as.matrix(wideDataTrain[,-c(1,50)]), partD_8h[,3], type.measure='mse', nfolds=10, family='gaussian', alpha=1)$lambda.min
praModel_8h<-glmnet(as.matrix(wideDataTrain[,-c(1,50)]),partD_8h[,3],alpha=1,family='gaussian',lambda = lambdaCalc)
predict_8h<-predict(praModel_8h, newx= as.matrix(wideTestData[,-c(1)]))

lambdaCalc<-cv.glmnet(as.matrix(wideDataTrain[,-c(1,50)]), partD_9h[,3], type.measure='mse', nfolds=10, family='gaussian', alpha=1)$lambda.min
praModel_9h<-glmnet(as.matrix(wideDataTrain[,-c(1,50)]),partD_9h[,3],alpha=1,family='gaussian',lambda = lambdaCalc)
predict_9h<-predict(praModel_9h, newx= as.matrix(wideTestData[,-c(1)]))

lambdaCalc<-cv.glmnet(as.matrix(wideDataTrain[,-c(1,50)]), partD_10h[,3], type.measure='mse', nfolds=10, family='gaussian', alpha=1)$lambda.min
praModel_10h<-glmnet(as.matrix(wideDataTrain[,-c(1,50)]),partD_10h[,3],alpha=1,family='gaussian',lambda = lambdaCalc)
predict_10h<-predict(praModel_10h, newx= as.matrix(wideTestData[,-c(1)]))

lambdaCalc<-cv.glmnet(as.matrix(wideDataTrain[,-c(1,50)]), partD_11h[,3], type.measure='mse', nfolds=10, family='gaussian', alpha=1)$lambda.min
praModel_11h<-glmnet(as.matrix(wideDataTrain[,-c(1,50)]),partD_11h[,3],alpha=1,family='gaussian',lambda = lambdaCalc)
predict_11h<-predict(praModel_11h, newx= as.matrix(wideTestData[,-c(1)]))

lambdaCalc<-cv.glmnet(as.matrix(wideDataTrain[,-c(1,50)]), partD_12h[,3], type.measure='mse', nfolds=10, family='gaussian', alpha=1)$lambda.min
praModel_12h<-glmnet(as.matrix(wideDataTrain[,-c(1,50)]),partD_12h[,3],alpha=1,family='gaussian',lambda = lambdaCalc)
predict_12h<-predict(praModel_12h, newx= as.matrix(wideTestData[,-c(1)]))

lambdaCalc<-cv.glmnet(as.matrix(wideDataTrain[,-c(1,50)]), partD_13h[,3], type.measure='mse', nfolds=10, family='gaussian', alpha=1)$lambda.min
praModel_13h<-glmnet(as.matrix(wideDataTrain[,-c(1,50)]),partD_13h[,3],alpha=1,family='gaussian',lambda = lambdaCalc)
predict_13h<-predict(praModel_13h, newx= as.matrix(wideTestData[,-c(1)]))

lambdaCalc<-cv.glmnet(as.matrix(wideDataTrain[,-c(1,50)]), partD_14h[,3], type.measure='mse', nfolds=10, family='gaussian', alpha=1)$lambda.min
praModel_14h<-glmnet(as.matrix(wideDataTrain[,-c(1,50)]),partD_14h[,3],alpha=1,family='gaussian',lambda = lambdaCalc)
predict_14h<-predict(praModel_14h, newx= as.matrix(wideTestData[,-c(1)]))

lambdaCalc<-cv.glmnet(as.matrix(wideDataTrain[,-c(1,50)]), partD_15h[,3], type.measure='mse', nfolds=10, family='gaussian', alpha=1)$lambda.min
praModel_15h<-glmnet(as.matrix(wideDataTrain[,-c(1,50)]),partD_15h[,3],alpha=1,family='gaussian',lambda = lambdaCalc)
predict_15h<-predict(praModel_15h, newx= as.matrix(wideTestData[,-c(1)]))

lambdaCalc<-cv.glmnet(as.matrix(wideDataTrain[,-c(1,50)]), partD_16h[,3], type.measure='mse', nfolds=10, family='gaussian', alpha=1)$lambda.min
praModel_16h<-glmnet(as.matrix(wideDataTrain[,-c(1,50)]),partD_16h[,3],alpha=1,family='gaussian',lambda = lambdaCalc)
predict_16h<-predict(praModel_16h, newx= as.matrix(wideTestData[,-c(1)]))

lambdaCalc<-cv.glmnet(as.matrix(wideDataTrain[,-c(1,50)]), partD_17h[,3], type.measure='mse', nfolds=10, family='gaussian', alpha=1)$lambda.min
praModel_17h<-glmnet(as.matrix(wideDataTrain[,-c(1,50)]),partD_17h[,3],alpha=1,family='gaussian',lambda = lambdaCalc)
predict_17h<-predict(praModel_17h, newx= as.matrix(wideTestData[,-c(1)]))

lambdaCalc<-cv.glmnet(as.matrix(wideDataTrain[,-c(1,50)]), partD_18h[,3], type.measure='mse', nfolds=10, family='gaussian', alpha=1)$lambda.min
praModel_18h<-glmnet(as.matrix(wideDataTrain[,-c(1,50)]),partD_18h[,3],alpha=1,family='gaussian',lambda = lambdaCalc)
predict_18h<-predict(praModel_18h, newx= as.matrix(wideTestData[,-c(1)]))

lambdaCalc<-cv.glmnet(as.matrix(wideDataTrain[,-c(1,50)]), partD_19h[,3], type.measure='mse', nfolds=10, family='gaussian', alpha=1)$lambda.min
praModel_19h<-glmnet(as.matrix(wideDataTrain[,-c(1,50)]),partD_19h[,3],alpha=1,family='gaussian',lambda = lambdaCalc)
predict_19h<-predict(praModel_19h, newx= as.matrix(wideTestData[,-c(1)]))

lambdaCalc<-cv.glmnet(as.matrix(wideDataTrain[,-c(1,50)]), partD_20h[,3], type.measure='mse', nfolds=10, family='gaussian', alpha=1)$lambda.min
praModel_20h<-glmnet(as.matrix(wideDataTrain[,-c(1,50)]),partD_20h[,3],alpha=1,family='gaussian',lambda = lambdaCalc)
predict_20h<-predict(praModel_20h, newx= as.matrix(wideTestData[,-c(1)]))

lambdaCalc<-cv.glmnet(as.matrix(wideDataTrain[,-c(1,50)]), partD_21h[,3], type.measure='mse', nfolds=10, family='gaussian', alpha=1)$lambda.min
praModel_21h<-glmnet(as.matrix(wideDataTrain[,-c(1,50)]),partD_21h[,3],alpha=1,family='gaussian',lambda = lambdaCalc)
predict_21h<-predict(praModel_21h, newx= as.matrix(wideTestData[,-c(1)]))

lambdaCalc<-cv.glmnet(as.matrix(wideDataTrain[,-c(1,50)]), partD_22h[,3], type.measure='mse', nfolds=10, family='gaussian', alpha=1)$lambda.min
praModel_22h<-glmnet(as.matrix(wideDataTrain[,-c(1,50)]),partD_22h[,3],alpha=1,family='gaussian',lambda = lambdaCalc)
predict_22h<-predict(praModel_22h, newx= as.matrix(wideTestData[,-c(1)]))

lambdaCalc<-cv.glmnet(as.matrix(wideDataTrain[,-c(1,50)]), partD_23h[,3], type.measure='mse', nfolds=10, family='gaussian', alpha=1)$lambda.min
praModel_23h<-glmnet(as.matrix(wideDataTrain[,-c(1,50)]),partD_23h[,3],alpha=1,family='gaussian',lambda = lambdaCalc)
predict_23h<-predict(praModel_23h, newx= as.matrix(wideTestData[,-c(1)]))

lambdas<-rbind(praModel_0h$lambda,praModel_1h$lambda,praModel_2h$lambda,praModel_3h$lambda,praModel_4h$lambda,praModel_5h$lambda,praModel_6h$lambda,praModel_7h$lambda,praModel_8h$lambda,praModel_9h$lambda,praModel_10h$lambda,praModel_11h$lambda,praModel_12h$lambda,praModel_13h$lambda,praModel_14h$lambda,praModel_15h$lambda,praModel_16h$lambda,praModel_17h$lambda,praModel_18h$lambda,praModel_19h$lambda,praModel_20h$lambda,praModel_21h$lambda,praModel_22h$lambda,praModel_23h$lambda)
```

Lambda values for each hour (starting from 00.00 to 23.00) are as follows:

```{r}
lambdas

mapePartD_0h<-mape(predict_0h,tempPartD_0h[,3])
mapePartD_1h<-mape(predict_1h,tempPartD_1h[,3])
mapePartD_2h<-mape(predict_2h,tempPartD_2h[,3])
mapePartD_3h<-mape(predict_3h,tempPartD_3h[,3])
mapePartD_4h<-mape(predict_4h,tempPartD_4h[,3])
mapePartD_5h<-mape(predict_5h,tempPartD_5h[,3])
mapePartD_6h<-mape(predict_6h,tempPartD_6h[,3])
mapePartD_7h<-mape(predict_7h,tempPartD_7h[,3])
mapePartD_8h<-mape(predict_8h,tempPartD_8h[,3])
mapePartD_9h<-mape(predict_9h,tempPartD_9h[,3])
mapePartD_10h<-mape(predict_10h,tempPartD_10h[,3])
mapePartD_11h<-mape(predict_11h,tempPartD_11h[,3])
mapePartD_12h<-mape(predict_12h,tempPartD_12h[,3])
mapePartD_13h<-mape(predict_13h,tempPartD_13h[,3])
mapePartD_14h<-mape(predict_14h,tempPartD_14h[,3])
mapePartD_15h<-mape(predict_15h,tempPartD_15h[,3])
mapePartD_16h<-mape(predict_16h,tempPartD_16h[,3])
mapePartD_17h<-mape(predict_17h,tempPartD_17h[,3])
mapePartD_18h<-mape(predict_18h,tempPartD_18h[,3])
mapePartD_19h<-mape(predict_19h,tempPartD_19h[,3])
mapePartD_20h<-mape(predict_20h,tempPartD_20h[,3])
mapePartD_21h<-mape(predict_21h,tempPartD_21h[,3])
mapePartD_22h<-mape(predict_22h,tempPartD_22h[,3])
mapePartD_23h<-mape(predict_23h,tempPartD_23h[,3])

mapePartD<-rbind(mapePartD_0h,mapePartD_1h,mapePartD_2h,mapePartD_3h,mapePartD_4h,mapePartD_5h,mapePartD_6h,mapePartD_7h,mapePartD_8h,mapePartD_9h,mapePartD_10h,mapePartD_11h,mapePartD_12h,mapePartD_13h,mapePartD_14h,mapePartD_15h,mapePartD_16h,mapePartD_17h,mapePartD_18h,mapePartD_19h,mapePartD_20h,mapePartD_21h,mapePartD_22h,mapePartD_23h)
mapePartD
```

Above, we can see the Mape results for each hour. First of all, when we compare these results with Part C, we can say that the Mape values dramatically decrease for every hour. This means that penalized regression model is better than the linear regression model. We observe a similar difference between working hours and night hours like in Part C. It is possible to say that this regression model is almost excellent because the Mape values are very low.

We do not observe any relation between lambdas and Mape values.

## PART E


## PART F

The figure below shows the comparison of different approaches used in this assignment. It is a nice visualization to decide which one is the best or the worst.

```{r}
boxplot(mape_lag48,mape_lag168,mapePartB,mapePartC, mapePartD , names = c("Lag_48","Lag_168","Part B","Part C","Part D"), xlab = "Approaches" , ylab = "Mape Values (%)")
```

If we really want to know whether our predictions are good or not, we have to compare them with the naive approaches. Those predictions with the naive approach can be seen as a baseline. Therefore, we see that the regression model we used in Part D (lasso regression) is the best and is very effective. The main reason for lasso regression having the best performance is because it uses penalized approach.

All in all, it is obvious that there are other regression models or approaches which are better than the naive approach. Thus, for predictions, regression algorithms, especially with penalties, must be used to make really good predictions.


Also, we can observe that the naive approach Lag_48 has the worst prediction performance. This was expected.
